Notebook of learning from ensemble labels

### 2021-07-04 docs/notebook_learn_dl_ensemble.Rmd
Update documentation :memo:

### Google Colab
In general, we mean to use Google Colab to run the model. For this case, it is more convenient to read the data locally and pickle them. Then directly load the pickles into Google Colab and just use the GPU environment to run the models.

@@

- U-net, which has simple architecture and is friendly to small dataset. This model is especially suitable for guess training.

- Deeplab3plus with ResNet as backbone. This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage. This model is super useful for the final train with manually corrected labels.

### Strategies to deal with noisy labels

@@

[NEED MORE EXPERIMENTS]

@@

- <input type="checkbox" checked> Learning rate and learning rate scheduler</input>
- Batch size
- Optimizer
- Model (U-net or Deeplab)
- Transform methods (if necessary)

@@

- Co_teaching works good. "Discuss" mode works slightly better than "argue" mode.

>>>>

#### Other useful commands

##### Check disk space and clean trash

```bash
df -H
cd .local/share/Trash/
rm -rf *
```
##### Check the RAM usage in M

```bash
free -m
```

@@

- U-net, which has simple architecture and is friendly to small dataset.

- Deeplab3plus with ResNet as backbone. This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage.

### Possible strategies to deal with noisy labels

@@

So after all experiments, we decide to stick with co-teaching & co-teaching-plus.

@@

- <input type="checkbox" checked> Learning rate and learning rate scheduler</input>
- <input type="checkbox" checked> Batch size</input>
- <input type="checkbox" checked> Optimizer</input>
- <input type="checkbox" checked> Model (U-net or Deeplab)</input>
- Transform methods (if necessary)

@@

- Co_teaching works good. "Discuss" mode works slightly better than "argue" mode. Since "argue" mode use the disagreement between two models, we assume this method would be helpful to transfer a model to other areas. Of course, this assumption needs more test.
